Effective Reionization Likelihood from Planck 2018 Data (?)

### 2021-03-22 paper/rei.tex

\begin{figure}[ht]
\includegraphics[width=0.48\textwidth]{paper/plots/pl18_taugtz_pc_zmax30_pl18_srollv2_with_and_without_physicality_prior.pdf}
\caption{Comparison of the 68\% and 95\% C.L. constraints on the cumulative optical depth $\tau(z, \zmax)$ from PC chains with (shaded) and without (black) applying the physicality prior. While the lower limits on $\tau(z, \zmax)$ are lowered when more unphysical models are included, the upper limits do not vary significantly (slightly lowered).  The total $\tau$ distribution is broadened only toward the lower $\tau$. \ch{Discuss in text the small difference in upper limits at $\tau(15, \zmax)$ is such that if one could remove unphysical models inside our current prior range, $\tau(15, \zmax)$ upper limit would be only slightly looser.} 
\wh{drop the ``with prior" label since with prior is our default approach}
}
% no prior: 95\% C.L.  = [-0.01935756790924691, 0.021029019067727237]
% with prior: {'z': 15, 'mean': 0.00694422689213187, 'std': 0.007568921831067864, 'limit68': [-0.0007215571045808687, 0.014684826477572082], 'limit95': [-0.006316156744039184, 0.02284538046347211]}
%
%}
\label{fig:plot_taugtz_2018_with_vs_without_physicality_prior}
\end{figure}

>>>>

\begin{figure}[ht]
\includegraphics[width=0.48\textwidth]{paper/plots/pl18_taugtz_pc_zmax30_pl18_srollv2_with_and_without_physicality_prior.pdf}
\caption{Comparison of the 68\% and 95\% C.L. constraints on the cumulative optical depth $\tau(z, \zmax)$ from PC chains with (shaded) and without (black) applying the physicality prior. While the lower limits on $\tau(z, \zmax)$ are lowered when more unphysical models are included, the upper limits do not vary significantly (slightly lowered).  The total $\tau$ distribution is broadened only toward the lower $\tau$. \ch{Discuss in text the small difference in upper limits at $\tau(15, \zmax)$ is such that if one could remove unphysical models inside our current prior range, $\tau(15, \zmax)$ upper limit would be only slightly looser.} 
}
% no prior: 95\% C.L.  = [-0.01935756790924691, 0.021029019067727237]
% with prior: {'z': 15, 'mean': 0.00694422689213187, 'std': 0.007568921831067864, 'limit68': [-0.0007215571045808687, 0.014684826477572082], 'limit95': [-0.006316156744039184, 0.02284538046347211]}
%
%}
\label{fig:plot_taugtz_2018_with_vs_without_physicality_prior}
\end{figure}
